\documentclass{article}
\title{Build a web site for representing international conferences}
\author{Abdelmalek Fathi, Maamar Choukri\\
Laarbi Tebessi Tebessa University\\
Math and Computer Science Departement}
\date{}
\begin{document}
	\maketitle
	\section{Introduction}
	\subsection{What ?}
	\paragraph{}
	Implementation of a web site for representing international conferences, demand submissions on them, and give all services for the subscribers.
	\subsection{Why ?}
	\paragraph{}
	The main reason of implementation this project is building Algerian web site for conferences.
	\subsection{Future Development}
	\paragraph{}
	In case of success of the project, we will develop this features:
	\begin{itemize}
		\item Online Conferences.
		\item Online Payment.
		\item Extended to be a web site for general scientific search
	\end{itemize}
	\newpage
	\section{Used tools}
	\subsection{Front-End}
	\paragraph{}
	Front-end is the client side programming (Graphical Interface) with HTML, CSS, JS and their frameworks like (Bootstrap, JQuery, React...).
	\subsubsection{HTML}
	\paragraph{}
	The HyperText Markup Language, or HTML is the standard markup language for documents designed to be displayed in a web browser. It can be assisted by technologies such as Cascading Style Sheets (CSS) and scripting languages such as JavaScript.
	\subsubsection{CSS}
	\paragraph{definition 1}
	Cascading Style Sheets (CSS) is a style sheet language used for describing the presentation of a document written in a markup language such as HTML. CSS is a cornerstone technology of the World Wide Web, alongside HTML and JavaScript.
	\paragraph{definition 2}
	CSS stands for Cascading Style Sheets. It is a style sheet language which is used to describe the look and formatting of a document written in markup language. It provides an additional feature to HTML. It is generally used with HTML to change the style of web pages and user interfaces. It can also be used with any kind of XML documents including plain XML, SVG and XUL.
	\paragraph{}
	CSS is used along with HTML and JavaScript in most websites to create user interfaces for web applications and user interfaces for many mobile applications.
	\subsubsection{Javascript}
	\paragraph{}
	Javascript is a programming language that conforms to the ECMAScript specification.[9] JavaScript is high-level, often just-in-time compiled, and multi-paradigm. It has curly-bracket syntax, dynamic typing, prototype-based object-orientation, and first-class functions.
	\subsubsection{JQuery (Front-end Framework)}
	\paragraph{definition 1}
	jQuery is a fast, small, and feature-rich JavaScript library. It makes things like HTML document traversal and manipulation, event handling, animation, and Ajax much simpler with an easy-to-use API that works across a multitude of browsers. With a combination of versatility and extensibility, jQuery has changed the way that millions of people write JavaScript.
	\paragraph{definition 2}
	jQuery is a JavaScript library designed to simplify HTML DOM tree traversal and manipulation, as well as event handling, CSS animation, and Ajax. It is free, open-source software using the permissive MIT License.
	\paragraph{JQuery Features}
	Following are the important features of jQuery.
	\begin{itemize}
		\item HTML and CSS manipulation and event methods
		\item DOM manipulation and element selection
		\item Effects and Animations
		\item Utilities
		\item AJAX
		\item JSON parsing
		\item Extensibility through plug-ins
	\end{itemize}
	\paragraph{}
	JQuery is widely used in web development and being used by many of the biggest companies sash as (Google, Youtube, Microsoft, IBM, Netflix...)
	\subsubsection{Bootstrap}
	\paragraph{}
	Bootstrap is a free and open-source CSS framework directed at responsive, mobile-first front-end web development. It contains CSS- and (optionally) JavaScript-based design templates for typography, forms, buttons, navigation, and other interface components.
	\subsubsection{Font Awesome}
	\paragraph{}
	Font Awesome is a font and icon toolkit based on CSS and Less. It was made by Dave Gandy for use with Bootstrap, and later was incorporated into the BootstrapCDN. Font Awesome has a reported 38\% market share among those websites that use third-party font scripts on their platform, ranking it second place after Google Fonts.
	\subsection{Back-End}
	\paragraph{}
	Back-end is the server side programming and database management, its work under the scene so the client can't see it.
	\subsubsection{Django (Back-end Framework)}
	\paragraph{definition 1}
	Django is a high-level Python Web framework that encourages rapid development and clean, pragmatic design. Built by experienced developers, it takes care of much of the hassle of Web development, so you can focus on writing your app without needing to reinvent the wheel. It’s free and open source.
	\paragraph{definition 2}
	is a Python-based free and open-source web framework that follows the model-template-views (MTV) architectural pattern. It is maintained by the Django Software Foundation (DSF).
	\paragraph{Advantages of Django}
	Here are few advantages of using Django which can be listed out here.
	\begin{itemize}
		\item Extremely fast and very secured
		\item Object-Relational Mapping (ORM) Support
		\item Multilingual Support
		\item Support for Ajax, RSS, Caching and various other front-end frameworks
		\item Built-in ready-to-use Administration Panel
		\item Developement Environment
		\item comes with a lightweight web server
		\item hug community
		\item and mush more...
	\end{itemize}
	\paragraph{}
	Django framework is widely used and many big web sites are build with it, like (Youtube, Instagrame, Spotify, Dropbox...)
	\subsubsection{MySQL}
	\paragraph{}
	 A relational database organizes data into one or more data tables in which data types may be related to each other; these relations help structure the data. SQL is a language programmers use to create, modify and extract data from the relational database, as well as control user access to the database. In addition to relational databases and SQL, an RDBMS like MySQL works with an operating system to implement a relational database in a computer's storage system, manages users, allows for network access and facilitates testing database integrity and creation of backups.
	\subsubsection{Firebase}
	\paragraph{}
	Firebase is a platform developed by Google for creating mobile and web applications. It was originally an independent company founded in 2011. In 2014, Google acquired the platform and it is now their flagship offering for app development.
	\section{Implementation}
	\section{Conclusion}
	\newpage
	\section{Bibliography}
	\begin{itemize}
		\item https://en.wikipedia.org/wiki/HTML
		\item https://en.wikipedia.org/wiki/CSS
		\item https://www.javatpoint.com/what-is-css
		\item https://en.wikipedia.org/wiki/JavaScript
		\item https://jquery.com/
		\item https://en.wikipedia.org/wiki/JQuery
		\item https://www.javatpoint.com/what-is-jquery
		\item https://en.wikipedia.org/wiki/Bootstrap\_(front-end\_framework)
		\item https://en.wikipedia.org/wiki/Font\_Awesome
		\item https://www.djangoproject.com/
		\item https://en.wikipedia.org/wiki/Django\_(web\_framework)
		\item https://www.tutorialspoint.com/django/django\_basics.htm
		\item https://en.wikipedia.org/wiki/MySQL
		\item https://en.wikipedia.org/wiki/Firebase
	\end{itemize}
\end{document}
